Fractional Types

### 2019-11-22 fracGC/p.tex
more readable parity code

We illustrate the new style of ancilla management with an interesting
example used in quantum circuits as a dynamic assertion of
entanglement~\cite{DBLP:journals/cal/ZhouB19}:

\begin{wrapfigure}[0]{r}{0.2\textwidth}
  \input{parity.tikz}
\end{wrapfigure}
\PIFDparity{}

>>>>

\begin{wrapfigure}{r}{0.2\textwidth}
  \input{parity.tikz}
\end{wrapfigure}
We illustrate the new style of ancilla management with an interesting
example used in quantum circuits as a dynamic assertion of
entanglement~\cite{DBLP:journals/cal/ZhouB19}:

\PIFDparity{}
